### 2015-07-27 doc/manual/runs.tex
Default magneticDriftDerivativeScheme now 3. Bugfix in sfincsScan_3

\section{Parallelization}
Choosing the number of nodes and procs.

>>>>

\section{Poloidal and toroidal magnetic drifts}

You can choose to either include or not include the poloidal and toroidal magnetic drifts.
These drifts are turned off by default.  To turn them on, all you need to do is
set \parlink{magneticDriftScheme} = 1 in the {\ttfamily \hyperref[sec:physicsParameters]{physicsParameters}} namelist.
If on, you must use VMEC
geometry (\parlink{geometryScheme} = 5).  The magnetic drift terms introduce nonzeros in the system matrix,
and therefore increase the memory required for factorization; a typical increase is 30-40\%.

\section{Parallelization}
[Coming soon...] Choosing the number of nodes and procs.
